My title\thanks{Code and data are available at: LINK.}

### 2024-02-08 paper/paper.tex
pdfs

\begin{document}
\maketitle
\begin{abstract}
First sentence. Second sentence. Third sentence. Fourth sentence.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[frame hidden, sharp corners, interior hidden, borderline west={3pt}{0pt}{shadecolor}, breakable, enhanced, boxrule=0pt]}{\end{tcolorbox}}\fi

>>>>

\begin{document}
\maketitle
\begin{abstract}
First sentence. Second sentence. Third sentence. Fourth sentence.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, enhanced, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, frame hidden, interior hidden, breakable]}{\end{tcolorbox}}\fi
